\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{textcomp}
\usepackage[document]{ragged2e}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Dasun Pubudumal - CV},
    pdfpagemode=FullScreen,
    pdfauthor={Dasun Pubudumal},     % author
    pdfsubject={CV},   % subject of the document
    pdfcreator={Dasun Pubudumal},   % creator of the document
    pdfproducer={Latex},  % producer of the document
    }

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \justify{\textbf{#1}{: #2 \vspace{-2pt}}}
  }
}

\newcommand{\resumeItemSingle}[1]{
  \item\small{
    {\justify{#1} \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\usepackage[medium]{HindMadurai}
\usepackage[T1]{fontenc}

\begin{document}


%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Dasun Pubudumal}}\\\\
  Portfolio: \href{https://dasunpubudumal.github.io}{dasunpubudumal.github.io} & Email: \href{mailto:}{~dasunpubudu94@gmail.com}\\
  Linkedin: \href{https://medium.com/@dasunpubudumal}{@dasunpubudumal} & Mobile: +9(471) 214-3308~~~~~~~~~~~~~~~~~~~~ \\
  Github: \href{https://github.com/xprilion}{~~~github.com/dasunpubudumal} \\
  Medium: \href{https://www.linkedin.com/in/dasun-pubudumal}{~dasun-pubudumal} \\
\end{tabular*}

\vspace{10pt}
A knowledge-seeking individual who believes in perseverance and skill. Well-versed and experienced in object-oriented paradigms, clean back-end code, and agile software development practices. Looking towards taking the next steps forward to broaden the horizons through teamwork and ceaseless diligence. 
\vspace{5pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Moratuwa}{Colombo, Sri Lanka}
      {Bachelor of Science, Department of Computer Science \& Engineering}{January 2016 - December 2020}
      \vspace{3pt}
      % {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Object-Oriented Programming, Databases}}}
    \resumeSubheading
      {Ananda College}{Colombo, Sri Lanka}
      {GCE Advanced Levels}{2014}
      % {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Object-Oriented Programming, Databases}}}
    \resumeSubHeadingListEnd
	    
\vspace{3pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~Java, Python, JavaScript, SQL}
	\resumeSubItem{Frameworks}{~~Spring Boot / Spring, NodeJS, Angular, React}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~~Maven, Docker, GIT, CI/CD, Kubernetes}
	\resumeSubItem{Platforms}{~~~~~~~AWS, Linux, Web}
	\resumeSubItem{Soft Skills}{~~~~~~Writing, Reading, Leadership}

\resumeSubHeadingListEnd
\vspace{5pt}
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading{\href{https://unibench.com.au/}{Unibench}}{Colombo, Sri Lanka}
    {Software Engineer (Full-time)}{June 2022 - June 2023}
    
	\vspace{7pt}
    \textbf{Experience}
        \resumeItemListStart
            \resumeItemSingle{Providing development services for an Australian (AU) organization that provides payment solutions for the AU region.}
            \resumeItemSingle{Using \href{https://aws.amazon.com/dynamodb/}{Amazon DynamoDB}: a NoSQL database as a centralized data store.}
            \resumeItemSingle{Hands-on involvement on developing \& deploying \href{https://aws.amazon.com/lambda/}{AWS Lambda} functions.}
            \resumeItemSingle{Performing technical spikes in accessing the feasibility of integrating new libraries such as \href{https://quarkus.io/}{Quarkus} into the existing platform.}
            \resumeItemSingle{Building new components from scratch, and extending the components with build jobs using \href{https://aws.amazon.com/codebuild/}{CodeBuild}, and \href{https://aws.amazon.com/codeartifact/}{CodeArtifact}.}
            \resumeItemSingle{Usage of asynchronous messaging with tools such as \href{https://aws.amazon.com/sqs/}{Amazon SQS}, and synchronous messaging using the \href{https://aws.amazon.com/api-gateway/}{API Gateway} REST API.}
            \resumeItemSingle{Adhering to Test Driven Development (TDD) to streamline development of production-grade payment systems.}
            \resumeItemSingle{Refactoring legacy code-bases to proper unit-testable code that adheres to properly-standardized conventions.}
            \resumeItemSingle{Used \href{https://react.dev/}{React} as a front-end library to develop a payment website (a Hosted Payment Page (HPF)) that interfaces first-hand with the customer.}
            \resumeItemSingle{Assisting the Automated Integration Test (AIT) procedures in the QA process.}
            \resumeItemSingle{Working with a team of experienced developers in which all of them were actively involved in the decision making process.}
            \resumeItemSingle{Using \href{https://www.atlassian.com/software/confluence}{Confluence} as a centralized Documentation Hub including design diagrams, local standards, and how-to guides.}
            \resumeItemSingle{Actively participating in Scrum Project Management tasks such as Sprint Retrospectives and Planning.}
            \resumeItemSingle{Experienced the incremental change of processes from working under a start-up organisation growing to a fully-functioning organisation that operates in scale.}
        \resumeItemListEnd

    \vspace{7pt}
    \textbf{Projects}
        \resumeItemListStart
            \resumeItem{MY PINPAD\textsuperscript \textregistered\ Integration}
              {Integration of Payment Terminals into the payment platform. Took the lead on on the terminal registration process that involved a back-end that performs the registration process in combination with a User Interface provided to the merchant.}
            \resumeItem{Credit-card Surcharging Integration}
              {Assisted in integrating the surcharging facility for credit card payments. This required integrating the surcharging front-end API calls into the Hosted Payment Page (HPF) provided by the organization, processing them in the back-end and proxying the relevant calls to the third party API.}
            \resumeItem{Receipt Generation for Advice Messages}
              {Took the lead in developing the receipts for a declared set of merchants upon receipt of the advice messages (an equivalent form of a web-hook) from a third-party payment system.}
            \resumeItem{Palms Integration for Direct Debit}
              {One of the platform's providers for Direct Debit payments. Assisted in converting a synchronous system to a queue-based asynchronous solution that caters for a slower third-party consumer.}
        \resumeItemListEnd

    \vspace{5pt}
  
    \resumeSubheading{\href{https://codegen.co.uk/}{CodeGen International}}{Colombo, Sri Lanka}
    {Software Engineer (Full-time)}{February 2020 - June 2022}

    \vspace{7pt}
    \textbf{Experience}
        \resumeItemListStart
            \resumeItemSingle{Designing, implementing and maintaining solutions for real-world problems in the Travel Domain.}
            \resumeItemSingle{Conducting sessions on the solutions to a wider reach, including publishing in \href{https://medium.com/@dasunpubudumal}{medium.com} and \href{https://www.travolution.com/news/in-depth/guest-posts/guest-post-how-ai-can-offset-the-costs-of-hotel-supply-data-duplication/}{travolution.com}.}
            \resumeItemSingle{Handling DevOps tasks such as CI/CD (i.e., integration and deployments).}
            \resumeItemSingle{Conducting knowledge-sharing sessions to crowds within and outside the organization.}
            \resumeItemSingle{Conducting performance tests using tools such as \href{https://www.yourkit.com/}{YourKit}, \href{https://visualvm.github.io/}{VisualVM}, Observability tools like \href{https://grafana.com/}{Grafana} and \href{https://www.elastic.co/kibana/}{Kibana} and in-built mechanisms such as Heap Dumps (\texttt{hprofs}).}
            \resumeItemSingle{Using \href{https://angular.io/}{Angular} as a front-end framework to update User Interfaces.}
            \resumeItemSingle{Leading a team of junior (intern) developers for major releases.}
            \resumeItemSingle{Effectively coordinating with other teams on the integration of the solutions developed.}
            \resumeItemSingle{Planning the backlog and prioritizing the tasks for major releases.}
            \resumeItemSingle{Introducing assistive technologies such as \href{https://developer.hashicorp.com/consul/docs/dynamic-app-config/kv}{Consul} for Configuration Management and \href{https://www.fluentd.org/}{Fluentd} for Log Aggregation.}
            \resumeItemSingle{Researching multiple solutions, conduct feasibility studies, and communicating the conclusions across the organisation.}
            \resumeItemSingle{Solving reported bugs including critical scenarios in production/live environments with out-of-memory issues.}
        \resumeItemListEnd

    \vspace{7pt}
    \textbf{Projects}
        \resumeItemListStart
            \resumeItem{TravelBox\texttrademark\  TRITIUM}
              {Aggregation of inventories from multiples sources, \textit{de}-duplication and exposure of the inventories to the TravelBox\texttrademark\ internal API. Primary platform for \textit{de}-duping was developed using \texttt{scikit-learn} with Python. The de-duping procedure was designed for an asynchronous execution.}
              \resumeItem{INSPIRE Recommendation Engine}
              {Personalisation utility for production-grade systems where travel inventories are personalised with respect to the user's interests. A content-filtering algorithm was used for the recommendation process, involving a recommendation matrix. A separate, asynchronous procedure was used to extract meta-data out of the inventories, and couple them with user interests in a specific calculation. The API developed to expose the recommender sorted the products using a score calculated using the user interests and a combination of aforementioned meta-data.}
              \resumeItem{TravelBooker}{CodeGen's SaaS solution for TravelBox\texttrademark. Primarily involved in integrating existing travel modules in TravelBox\texttrademark\ to the SaaS solution.}
        \resumeItemListEnd
    \vspace{5pt}

    \resumeSubheading{\href{https://www.directfn.com/en/}{DirectFN LTD}}{Colombo, Sri Lanka}
    {Software Engineering Intern}{June 2018 - December 2018}
    
	\vspace{7pt}
    \textbf{Experience}
        \resumeItemListStart
            \resumeItemSingle{Worked with a very experienced set of Senior Software Engineers with established agile practices.}
            \resumeItemSingle{Assisted in developing a monitoring platform for the primary system.}
            \resumeItemSingle{Worked extensively with \href{https://spring.io/}{Spring Framework} with Dependency Injection with Inversion of Control (IoC).}
            \resumeItemSingle{Used WebSocket protocol for sending real-time data to the monitoring platform's visualization engine.}
            \resumeItemSingle{Research on Elasticsearch Logstash \& Kibana (ELK) stack on aggregation of logs \& processing them.}
        \resumeItemListEnd

    \vspace{7pt}
    \textbf{Projects}
        \resumeItemListStart
            \resumeItem{DFN Falcon}
              {Monitoring platform through which an additional layer of custom observability is provided for each individual module. Assisted in fixing some bugs and developing additional utilities related to the user interface and the back-end. Did some research on improving the system of processing logs.}
        \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{5pt}

\section{Publications}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Jointly Optimizing Sensing Pipelines for Multimodal Mixed Reality Interaction}{IEEE MASS}
    {\href{https://arxiv.org/abs/2010.06584}{DOI: 10.1109/MASS50613.2020.00046}}{2020}
\vspace{5pt}
  \resumeSubHeadingListEnd

\vspace{5pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {\textbf{Virtusa Award} for the best Semester 5 Project - May, 2018}

\end{description}

\vspace{5pt}
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Director of IT at Rotaract Club}{University of Moratuwa}
    {Project \href{https://blog.rotaractmora.org/tag/inspico/}{Inspico} (Project Chair), Project Hand in Hand and Content Creation.}{2018 - 2020}
\vspace{5pt}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \resumeSubheading
    {Director of IT at Rotaract Club Alumni}{University of Moratuwa}
    {Primarily responsible for maintaining the club \href{https://rotaractmora.org/}{website} and the blog.}{2019 - 2020}

\resumeSubHeadingListEnd

\end{document}
